Fluid structure interaction with ETVF

### 2022-12-08 manuscript/paper.tex
Add 3 cases for hs tank

\begin{abstract}
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
{XXX}, {XXX}, {XXX}

@@

@@

>>>>

\begin{abstract}
In the current work we have proposed a single
unified meshless particle based numerical scheme to model fluid structure
interaction problems. A corrected transport velocity formulation is utilised to
model both fluid and solid phases. Both the phases follow the same set of
governing equations. The corrected transport velocity formulation has proved
that it has better approximation in fluids due to the corrected terms as well
the particle distribution. We also take the advantage of the ctvf scheme in
eliminating the tensile instability of the structures. The coupling is
seamlessly done as both the phases are simulated in one configuration and no
reference frame or initial frame is used to model the dynamics of any phase.
Three numerical problems are simulated to show the current scheme validation. A
clamped beam acted upon by a uniformly distributed load, hydrostatic tank on an
elastic plate, and dam breaking flow hitting a plate.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
{Smoothed particle hydrodynamics}, {Fluid-structure interaction}, {Transport velocity formulation}

@@

\begin{itemize}
\item Fluid structure interaction in real life. Refer to papers where they deal
  with FSI problems, this includes FEM coupling, MPS coupling and many other
  paper, or may be looking at one review paper and select 5 paper to write about this.
\item In many different ways FSI is modeled, this includes mesh based and mesh
  less. Explain in a good detail what meshless methods are out there which
  handles these problems. This includes SPH too.
\item Explain different ways SPH is applied in FSI area. Detail some papers
  where how differently fluid as well as structures is modelled. This includes
  ISPH, WCSPH, TVF, delta+ SPH and for structures TLSPH, ULSPH, some other DEM
  methods. Also mention the latest multiphase flow, where air is considered,
  then mention the adaptive formulation, where the author captures the cavity.
  And what different coupling approaches are handled so far.
\item Mention the open source software which provide SPH formulation (This is
  optional for now).
\item Explain what we are going to do in the current work. We couple the
  transport velocity formulation approach extended to free surface to model
  both the phases.
\item Explain the examples.
\end{itemize}

@@

FSI is a common engineering problem that is seen in daily life. Few examples
include the deformation of the wind turbine blade due to the fluid flow, the
flow traversal due to the deflected blade, blood flow in heart value, coastal
engineering, and vortex-induced vibration
\cite{williamson2004vortex,bearman2011circular}. An accurate study FSI
phenomena can allow us to understand systems where FSI is prevalent. However,
studying the FSI phenomena through experiments or analytical techniques is
complex. The complexity arises due to the nonlinear behavior of the
fluid-structure coupling. Due to the difficulty in studying the FSI phenomena by
experiments and analytical methods, we resort to numerical study due to its
flexibility. Mesh-based and meshless methods are used to study the FSI phenomena
numerically.

Mesh-based schemes such as FEM \cite{lozovskiy2015unconditionally} and FVM
\cite{jasak2007updated} have been in the market for the last few decades
and are successful in modeling the FSI phenomena. But, mesh-based procedures are
not favorable when dealing with free surface flow problems and problems with
large deformation of solids due to large mesh distortion
\cite{moresi2003lagrangian}.

% Current research
% has been carried out to address such issues, and methods like Immersed Boundary
% Method \cite{mittal2005immersed} and level set method
% \cite{olsson2005conservative} are proposed to address such issues.

Therefore, meshless methods are used to solve free surface and large deformation
problems, which is advantageous in these areas. Among many meshless methods, we
often find Smoothed particle hydrodynamics (SPH) and Material point method (MPM)
to model the fluid phase, and the solids phase is modeled with DEM, RKPM, or SPH
itself \cite{hu2010material,li2022material}. These meshless techniques have
been coupled for the past two decades to model the fluid-structure interaction.
A few schemes with SPH and MPM are SPH-DEM, SPH-TLSPH, SPH-RKPM, SPH-PD,
MPM-DEM, MPM-RKPM \cite{khayyer2022systematic}. For more, see the review by
\cite{khayyer2022systematic}.%  In the current work, we use SPH alone to model
% fluid and solid phases.

In the SPH methods, fluids are modelled primarily using two different
approaches, one by assuming it to be weakly compressible and another by
considering it as incompressible.
% Though both techniques successfully model fluid dynamics, they have their
% drawbacks.
Weakly compressible SPH suffers from particle pairing and irregular particle
distribution problems affecting the function approximation.
\cite{xu2009accuracy} proposed a particle shifting technique, where particle
positions are adjusted after each timestep to distribute the particles
homogeneously. The particle properties are adjusted at the new position using
Taylor series approximation. Later, \cite{adami2013transport} proposed a
complete scheme where the particle transport is incorporated in Navier-Stokes
equations, and a new set of equations is solved and applied to internal fluid
flow problems. \cite{zhang_hu_adams17} extended the TVF formulation to GTVF
and solved free surface problems. \cite{adepu2021corrected}proposed a
corrected TVF scheme (CTVF) where the missing terms in TVF are incorporated to
solve the free surface flow problems.

If we consider papers where SPH alone is used to model the FSI phenomena, we
have WCSPH-Total Lagrangian SPH (TLSPH) \cite{zhan2019stabilized},
WCSPH-Updated Lagrangian SPH (ULSPH) \cite{antoci2007numerical},
ISPH-TLSPH\cite{salehizadeh2022coupled}. Where the coupling is handled
using \cite{Adami2013} conditions and adapted accordingly.
% So, in all these
% schemes we have fluid being modeled in updated frame and solid being simulated
% in a reference frame.
Modeling the FSI using a transport velocity formulation is at a great advantage
as it can solve the tensile instability issue in solid dynamics and inharmonious
particle distribution in fluids. We model both fluid and solid phase in CTVF and
couple them in the current work.

\section{Fluid }
